An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
caption Similarity matrices is changed

        \hspace{-3mm}
        \caption{Similarity matrices of the captured images in experimental results. Condensed fray shades point out to positive alikeness between scenes. The black lines in lower triangle indicates user specified ground truths. The gray lines in upper-triangle shows the obtained results.}
        \label{fig:dist_matrices}
\end{figure}

>>>>

        \hspace{-3mm}
        \caption{Similarity matrices of the captured images in experimental results. Condensed gray shades point out to positive alikeness between scenes. The black dots in lower triangle indicates detected loop closures at $90\%$ precision.}
        \label{fig:dist_matrices}
\end{figure}
